Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-05 draft.tex
1 more reference; improve MILP

\begin{itemize}
\item General motivation: need to deal with partially specified preferences and as well partially specified voting rules
\item Focus on positional scoring rules
\item Robust decision criterion: minimax regret
\item Incremental elicitation of preferences can help mitigating the cognitive and communication costs
\item Novelty of the proposed method
\item Structure of the paper
\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}
\end{itemize}

@@

% Add some general remarks about using minimax regret

\subsection{Computation of minimax regret}
In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \cite{Lu2011} so that we decompose the $\PMR$ into the contributions that is associated to each agent.
The settings is however more challenging due to the presence of uncertainty in the weights.

@@

We now  exploit the decomposition of the score in terms of votes.
The actual regret of choosing $x$ instead of $y$ can be written as:
\[
s(y; \profile,\w) - s(x; \profile, \w) = [\sum_{j=1}^n s(y; v_j,\w) - s(x; v_j,\w)]
\]
and  can rewrite $\PMR$ as follows:
\begin{align*}
\PMR(x,y; \pprofile, W) &= \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] = \\
&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [s(y; v_j,\w) - s(x; v_j,\w)]=\\
&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}] \\
\end{align*}
Given our hypothesis, for all pairs of alternatives, there exists completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights. 
That is, we can exhibit, for each voter $j$, a completion $v_j$ such that $\forall \w, \forall v'_j \in C(\ppref_j): [w_{v_j(y)} - w_{v_j(x)}] \geq [w_{v'_j(y)} - w_{v'_j(x)}]$.

@@

By solving a sequence of pairwise max regret computation is possible to determine the minimax regret solution.
Each PMR is computed using a linear program.
The decision variables correspond to the weights attached to the different positions.
Constraints are on the feasible parameters (the ``weights'' of the scoring rules); contraints represent the preferences of the chair about the scoring rule.

@@

\begin{itemize}
 	\item Mixed integer program to solve minimax regret without the convexity
 	\item Approximations ?
\end{itemize}

@@

Since the objective is to maximize pairwise regret

@@

We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
%Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.

\begin{align}
\max & \sum_{l=1}^m  V_{l}^{j,+} - V_{l}^{j,-}\\
\text{ s.t. } & \\
& V_{l}^{j} \leq I^j \\
& V_{l}^{j} \leq w_l \\
& V_{l}^{j} \leq I^j \\
& V_{l}^{j} \leq w_l 
\end{align}

@@

\begin{itemize}
	\item Minimax regret can be used to guide the elicitation process
	\item As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If optimality is derived, we can perform elicitation until minimax regret drops to zero.
	\item At each step, the system need to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule
	\item Type of questions that we can ask to the chair:
	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
\end{itemize}

>>>>

\begin{itemize}
\item General motivation: need to deal with partially specified preferences and as well partially specified voting rules
\item Focus on positional scoring rules
\item Robust decision criterion: minimax regret
\item Incremental elicitation of preferences can help mitigating the cognitive and communication costs
\item Novelty of the proposed method
\item Structure of the paper
\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, \cite{Xia2008}
\end{itemize}

@@

% Add some general remarks about using minimax regret
\subsection{Computation of minimax regret}
In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \cite{Lu2011} so that we decompose the $\PMR$ into the contributions that is associated to each agent.
The settings is however more challenging due to the presence of uncertainty in the weights.

@@

By exploiting the decomposition of the score in terms of votes, we write the actual regret of choosing $x$ instead of $y$ as:
\[
s(y; \profile,\w) - s(x; \profile, \w) = [\sum_{j=1}^n s(y; v_j,\w) - s(x; v_j,\w)]
\]
and  can rewrite $\PMR$ as follows:
\begin{align*}
\PMR(x,y; \pprofile, W) &= \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] = \\
&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [s(y; v_j,\w) - s(x; v_j,\w)]=\\
&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}] \\
\end{align*}
Given our hypothesis, for all pairs of alternatives, there exist completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights. 
That is, we can exhibit, for each voter $j$, a completion $v_j$ such that $\forall \w, \forall v'_j \in C(\ppref_j): [w_{v_j(y)} - w_{v_j(x)}] \geq [w_{v'_j(y)} - w_{v'_j(x)}]$.

@@

By solving a sequence of pairwise max regret computations is possible to determine the minimax regret solution.
Each PMR is computed using a linear program.
The decision variables correspond to the weights attached to the different positions.
Constraints are on the feasible parameters (the ``weights'' of the scoring rules); contraints represent the preferences of the chair about the scoring rule.

@@

\begin{itemize}	
	\item (will probably go to a later section, or to the appendix)
	\item Mixed integer program to solve minimax regret without the convexity
 	\item Approximations ?
\end{itemize}

@@

Since the objective is to maximize pairwise regret...

@@

We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
%Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.
 Finally, the following is the optimization problem that compute the value $\PMR$.
 The variables are $w$, $V$, $I$,...
\begin{align}
\max & \sum_{l=1}^m  V_{l}^{j,+} - V_{l}^{j,-}\\
\text{ s.t. } & w \in W  \\
& \sum_{l} I^{j}_{l} = 1 & \forall j \\
& V_{l}^{j,+} \leq I^j  & \forall l,j \\
& V_{l}^{j,+} \leq w_l & \forall l,j \\
& V_{l}^{j,-} \geq w + I^j - 1 & \forall l,j \\
& V_{l}^{j,-} \geq 0 & \forall l,j\\
\end{align} 
The optimization program can be solved by any suitable MILP solver.

@@

%regret-based incremental elicitation method
\begin{itemize}
	\item Minimax regret can be used to guide the elicitation process
	\item As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If optimality is derived, we can perform elicitation until minimax regret drops to zero.
	\item At each step, the system need to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule
	\item Type of questions that we can ask to the chair:
	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
\end{itemize}
